Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-17 paper.tex
reviewed section 3.3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Indeed, research in software verification is now incorporating such considerations, during checking processes, and some schemes already use knowledge about the system to be verified and the underlying hardware. Recently, a verification tool for digital systems was proposed, which is called digital system verifier (DSVerifier)~\cite{dsv_spin2015,Monteiro16} and is able to aid engineers to check overflow, limit cycle, output error, timing, stability, and minimum phase, considering finite word-length (FWL) effects. Additionally, DSVerifier checks closed-loop systems with uncertain models considering FWL effects, which are typically represented as hybrid systems, {\it i.e.}, the controller is digital but the controlled agent (plant) is a physical and continuous system~\cite{Bessa17}. That ultimately leads to the use of analog-to-digital converters, which are one of the most important aspects to be considered, given that data loss (quantization) is inevitable. As a consequence, verification procedures have to consider the interaction between a continuous plant and a digital (and sampled) controller with FWL effects, which can be connected using different control system configurations. Additionally, the latter may present a different behavior, regarding what was specified in analog domain, due to the inherent discret-time operation.

>>>>

Indeed, research in software verification is now incorporating such considerations, during checking processes, and some schemes already use knowledge about the system to be verified and the underlying hardware. Recently, a verification tool for digital systems was proposed, which is called digital system verifier (DSVerifier)~\cite{dsv_spin2015,Monteiro16} and is able to aid engineers to check overflow, limit cycle, output error, timing, stability, and minimum phase, considering FWL effects. Additionally, DSVerifier checks closed-loop systems with uncertain models considering FWL effects, which are typically represented as hybrid systems, {\it i.e.}, the controller is digital but the controlled agent (plant) is a physical and continuous system~\cite{Bessa17}. That ultimately leads to the use of analog-to-digital converters, which are one of the most important aspects to be considered, given that data loss (quantization) is inevitable. As a consequence, verification procedures have to consider the interaction between a continuous plant and a digital (and sampled) controller with FWL effects, which can be connected using different control system configurations. Additionally, the latter may present a different behavior, regarding what was specified in analog domain, due to the inherent discret-time operation.
